---
title: "DATA607_week9"
author: "Pei-Ming Chen"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

DATA607 Week 9  Assignment 
The New York Times web site provides a rich set of APIs, as described here: https://developer.nytimes.com/apis You’ll need to start by signing up for an API key.  Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it into an R DataFrame. 

```{r}
#install.packages("rjson")
#install.packages("keyring")
```

### Exercise 1

```{r }
library("jsonlite")
library("tidyverse")
library("dplyr")
library("ggplot2")
library("stringr")
library("httr")
library("keyring")
```


### Exercise 2

Insert any text here.

```{r }
# API Key
apikey <- "7ZbUeHfGPlUloCbyBLhJZmjo5DfAyyUo"

#Get the URL 
theURL <- paste("https://api.nytimes.com/svc/topstories/v2/books.json?api-key=7ZbUeHfGPlUloCbyBLhJZmjo5DfAyyUo")

dataA <- GET(theURL)
dataA

dataA$status_code
```

### Exercise 3

```{r}
summary(dataA)

```
### Exercise 4

```{r}
Bookstext <- content(dataA, as = "text")
```

### Data Frame

```{r}
Books_text_df <- Bookstext %>% 
  fromJSON() %>% 
  as.data.frame()

colnames(Books_text_df)

```
### Rename columnes 

```{r}
colnames(Books_text_df) = c("Status", "Copyright", "Section", "Updated","Number_of_results", "Res_Section", "subsection", "Title", "abstract", "Url", "Uri", "byline", "item_type", "updated_date", "created_date","published_date", "material_type_facet", "kicker", "des_facet", "org_facet", "per_facet", "geo_facet", "multimedia", "short_url")

colnames(Books_text_df)
```

```{r}
Number_of_results <- Books_text_df %>%
  group_by(Number_of_results) %>%
  summarise(num=n()) %>%
  arrange(desc(num))
head(Number_of_results)
  
```



###  Types and number of byline of the 34 articles were plotted below

```{r}
byline <- Books_text_df %>%
  group_by(byline) %>%
  summarise(num=n()) %>%
  arrange(desc(num))
byline

Books_text_df %>% ggplot(aes(y = byline)) + geom_bar()
```

### Abstracts of the 34 four articles were listed in a table below

```{r}
abstract <- Books_text_df %>%
  group_by(abstract) %>%
  summarise(num=n()) %>%
  arrange(desc(num))
head(abstract)
abstract

  
```

